Workflow of Inverse Model for Rooting Profiles

### 2020-04-11 Workflow.Rmd
added likelihood calculcation

```{r Chunk 3, eval = TRUE}
# This sources "code/4.2GLUErun_part2_func_BCI.R"
source("code/4.3.GLUErun_part2_BCI.R")
# splevel = "on"; goodness.fit = 0.3; drop.months = "Mar"
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "Feb")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "Mar")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "FebMar")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "Feb")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "Mar")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "FebMar")
```

@@

```{r Chunk 6, eval = TRUE}
source("code/4.7.summarising_udi_by_sp_size.R")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Feb")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "FebMar")
# # splevel = "on"; dryseason = "off"; rsq.thresh = 0.5; root.selection = "exp"; iso.subset = "off"
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Jan")

>>>>

```{r Chunk 3, eval = TRUE}
# This sources "code/4.2GLUErun_part2_func_BCI.R"
source("code/4.3.GLUErun_part2_BCI.R")
# splevel = "off"; goodness.fit = 0.3; drop.months = "Mar"
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "None")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "Jan")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "Feb")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "Mar")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "JanFeb")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "FebMar")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "JanFebMar")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "None")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "Jan")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "Feb")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "Mar")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "JanFeb")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "FebMar")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "JanFebMar")
```

@@

```{r Chunk 6, eval = TRUE}
source("code/4.7.summarising_udi_by_sp_size.R")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Feb")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "FebMar")
# # splevel = "on"; dryseason = "off"; rsq.thresh = 0.5; root.selection = "exp"; iso.subset = "off"
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Mar")
